Sampling Rate in the Dynamic Speckle Analysis

### 2019-09-06 article/article_1.tex
pronto para submeter

\journal{Optics Communications}

@@

\title{Sampling Frequency in the Dynamic Speckle Analysis}
%\tnotetext[mytitlenote]{Fully documented templates are available in the 
%elsarticle package on \href{http://www.ctan.org/tex-archive/macros/latex/contrib/elsarticle}{CTAN}.}

% Group authors per affiliation:
\author{Rivera, F. P.}
\author{Pe\~na, R. G.}
\author{Braga, R. A.}

@@

\begin{abstract}
In this article, we show as the variation of sampling frequency, 
in a dynamic speckle analysis, affects the value of some dynamic speckle index, 
to the cases of the absolute value of the differences index, the temporal 
speckle standard deviation index and the temporal 
speckle mean index.
We show that  the dynamic speckle index value change the maximum excursion with 
the variation of sampling frequency, affected directly by the time integration 
(exposition time) of camera.
We highlight the importance of knowing  the frequency band of analyzed phenomenon, 
in order to choose the appropriate sampling frequency, 
being recommendable to use the minimal sampling frequency possible
to get an acceptable maximum excursion, 
and an illumination level with good signal-noise ratio.

@@

\begin{keyword}
Sampling frequency \sep
Dynamic speckle index \sep 
Dynamic speckle index \sep 
Dynamic speckle analysis
\end{keyword}

@@

%3) Resgate a problematica( Importancia do problema de pesquisa - extenda primer passo)
Thus, 
it is necessary analyze the effect of technical parameters that affect the perceived illumination level; 
in these sense,
we analyze the effect of sampling frequency, 
and consequently the time exposure, in a dynamic laser speckle analysis
that use: the absolute value of the differences index, 
the temporal speckle standard deviation index and the temporal speckle mean index \cite{Nothdurft:05}.

%4) Relevancia do artigo(importancia para outros del artigo publicado)
Knowing the effect of sampling frequency over an index value,
a researcher will be able to have a criteria to choose the appropriate sampling frequency 
for a certain monitored phenomenon. 
% Thus,
% optimizing resources when choosing the hardware specification in a system setup; 
% being in this case, the limitations relatives to illumination level and signal-noise relation in the study sample.

%5) Anuncie a hipotesis
For this purpose, we show that given a dynamic speckle test, exists an appropriate frequency band
to the sampling frequency. High values of sampling rate may cause unintended consequences on the index value, 
such as the decrease of the excursion between two activity levels, given a determinate index value. 
In turn, decreasing the sampling frequency promoted by the increasing of the exposure time,
will cause a reduction of the temporal speckle contrast,
 and consequently limit the possibility  to get information from the sample.

@@

\subsection{Time exposure of the camera}
\label{subsec:expositiontime}
The sampling frequency ($F_s$) or acquisition time in frames per second ($fps$), 
in the camera Marlin F-033 is obtained using the 
 Table \ref{table:1}, 
\begin{table}[h!]
\centering
\begin{tabular}{||c c c c c||} 
 \hline
 $Shutter$ &  $Base$ [$\mu s$] & $Offset$ [$\mu s$] & $E$ [$ms$] & $F_s$ [$fps$]\\ [0.5ex] 
 \hline\hline
 3332  & 20  & 12  & 66.652  & 15.003  \\ 
 1665  & 20  & 12  & 33.312  & 30.019  \\ 
 1110  & 20  & 12  & 22.212  & 45.021  \\ 
 832   & 20  & 12  & 16.652  & 60.053  \\ [1ex] 
 \hline
\end{tabular}
\caption{Exposition time and sampling frequency}
\label{table:1}
\end{table}
where we can see the 4 sampling frequencies that will be used in the tests;
these values were obtained using  
the shutter register value ($Shutter$), 
the time base register value ($Base$),
the exposure time offset ($Offset$) and
the effective exposure time ($E$);
 so that the exposure time ($Exposure$),
\begin{equation}
Exposure= Shutter \times Base,
\end{equation}
\begin{equation}
\frac{1}{F_s}=E= Exposure + Offset.
\end{equation}
Where,  $F_s$ is calculated in relation to $E$; being that,
the $Exposure$ represent the photography integration time and $E$ the effective time
between photographs; 
the difference between these two exposures arise from $Offset$ time, 
that is the time between end and start of a photography.
In all cases the exposure time is much bigger than $Offset$; so, we can approximate
that $F_s\approx 1/Exposure$.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Figure \ref{fig:STDtest1} presents the $STD(t)$ index in the test showed in the 
Section \ref{subsec:test1}.
\begin{figure}[ht!]
    \centering
    \begin{subfigure}{0.48\textwidth}
        \caption{$STD$ index value.}
        \includegraphics[width=\textwidth]{FPS_f11_rawSTD.eps}
        \label{fig:stdraw}
    \end{subfigure}
    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
      %(or a blank line to force the subfigure onto a new line)
    \begin{subfigure}{0.48\textwidth}
        \caption{Normalized $STD$ index value.}
        \includegraphics[width=\textwidth]{FPS_f11_norm1STD.eps}
        \label{fig:stdnorm}
    \end{subfigure}
    \caption{$STD$ index anaysis.}\label{fig:STDtest1}
\end{figure}
The Figure \ref{fig:stdraw} shows the  behavior of $STD(t)$ index, in each time $t$, 
to 4 different sampling rates. Remembering that this index uses information in the entire frequency
band ($0$ until $F_s/2$ Hz), as seen in Section \ref{sec:std}.
This index shows a different behavior in time to each sampling frequency,
so that, the value of the index in each time  decreases in proportion with 
the grow of sampling rate. By other side,
Figure \ref{fig:stdnorm} shows a normalized version of $STD(t)$ index;
being the unit, the maximum value of curves; thus,
it can be seen that exists a small difference between the maximum excursion 
of the curves with different sampling rates; even so, it is possible to observe
a slight decrease of the maximum excursion in the curve with the grow of the sampling rate, 
unlike the $AVD(t)$ index.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Figure \ref{fig:STDFtest1}, presents the $STDF(t)$ index, in the test showed in the 
Section \ref{subsec:test1}.
\begin{figure}[ht!]
    \centering
    \begin{subfigure}{0.48\textwidth}
        \caption{$STDF$ index value.}
        \includegraphics[width=\textwidth]{FPS_f11_rawSTDF.eps}
        \label{fig:stdfraw}
    \end{subfigure}
    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
      %(or a blank line to force the subfigure onto a new line)
    \begin{subfigure}{0.48\textwidth}
        \caption{Normalized $STDF$ index value.}
        \includegraphics[width=\textwidth]{FPS_f11_norm1STDF.eps}
        \label{fig:stdfnorm}
    \end{subfigure}
    \caption{$STDF$ index anaysis.}\label{fig:STDFtest1}
\end{figure}
Figure \ref{fig:stdfraw} shows the behavior $STDF(t)$ index, in each time $t$, 
to 4 different sampling rates. Remembering that this index uses filtered 
information of datapack, so that the frequency
band is between $F_s/4$ and $F_s/2$ Hz. 
% of similar way of $AVD(t)$ index but with different order filter, as seen in Section \ref{sec:stdf}.
This index shows monotone decreasing behavior in time, where we observe 
a different behavior in time to each different sampling rate;
so that, the value of the index in each time decreases in proportion with 
the grow of sampling rate. By other side,
Figure \ref{fig:stdfnorm} shows a normalized version of $STDF(t)$ index;
being the unit, the maximum value of curves; thus,
it can be seen that exists a considerable difference between the maximum excursion 
of the curves with the use of sampling frequency; so, it is possible to observe a 
grow of the maximum excursion when the sampling rate decrease, like the $AVD(t)$ index.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Figure \ref{fig:MEANtest2} shows the $MEAN(t)$ index,
decreasing its value
%in the test described in the Section \ref{subsec:test2};
\begin{figure}[ht!]
    \centering
    \includegraphics[width=0.5\textwidth]{FPS_Semilla_3_3diasALLMEAN.eps}
    \caption{$MEAN$ index value in the germinated corn seed.}\label{fig:MEANtest2}
\end{figure}
%We observe as the index decrease your value, 
with the increment of sampling frequency, %in the datapack,
where from %so that between 
$15$ Hz to $60$ Hz, the index value reached the $20.137\%$ of its value.

@@

The matrices $STDB$ are represented using a color palette, 
that goes from dark blue (low values) to dark red color (high values), 
%representing of ascendant way 
linked to the values of activity,
%in each pixel in all matrices, as It is shown in the top of table. 
it is evident how the index values decreases with
the increment of frequency sampling $F_s$.
%in each one of 8 frequency bands, 
The index values also decrease with the increment of the position of frequency band,
being  a frequency band between $0$ Hz and $3.75$ Hz with a sampling rate of $15$ hz,
the better analysis's case; in the sense of better differentiating places of lower and higher index value.

@@

%In the results seen in Section \ref{sec:numericalresults}, we can observe in 
In the Figure \ref{fig:MEANtest1} and \ref{fig:MEANtest2}, 
%that 
the indexes show a relation between the profile of mean index curve and the sampling frequency of datapack. 
%How is known \cite{Nothdurft:05}, 
The temporal speckle mean index (Fig. \ref{fig:MEANtest1}) is related to 
the observed illumination level in the surface of the material \cite{Nothdurft:05} and  
correspond to the analysis of zero frequency components of signal.
%correspond to the offset in the frequency domain or frequency zero.
%zero frequency of the signal (datapack);
Thus, we can conclude that the level of illumination, perceived by the camera, 
decrease with the increment of sampling rate. 
This is because that the exposition time is modified with the alteration of sampling frequency to commercial cameras, 
%see Section \ref{subsec:expositiontime}, 
so that less lighting is used to take the picture and consequently the 
temporal speckle mean index decrease in  its value.
In this sense, it is important to be aware to choose a sampling frequency
that gives us an index value superior to the noise level of test or to the quantization level of the camera.

The modification of exposition time also affects  and limits other indexes,
remember that we have a quantization level between $0$ and $255$ in the camera. 
We can see this interference in the Figures \ref{fig:AVDtest1}, \ref{fig:STDtest1}, \ref{fig:STDFtest1} and \ref{fig:INDEXtest2}, 
where the $AVD(t)$, $STD(t)$ and $STDF(t)$ indexes decrease their values in concordance with the decrease of exposition time.
Other way in that  the sampling frequency affects the values of indexes,
can be seen in the limitation of
%It is that, it limits 
the frequency band of an analyzed signal; for example,
a sampling frequency $F_s$, by the Nyquist theorem \cite{Nyquist,Shannon}, 
causes  the limitation of  frequency band %of analyzed signal (datapack)  will be 
between $0 Hz$ and $F_s/2~Hz$.
Thus, in this context we have an index as $STD(t)$ that uses information between $\langle \left. 0, F_s/2 \right ] Hz$, 
while other  indexes as the $AVD(t)$ and the $STDF(t)$ index, use information of half frequency band, 
between $\left [ F_s/4, F_s/2 \right ] Hz$.
In the comparison between $STD(t)$ vs  $\{$ $STDF(t)$ and $AVD(t)$ $\}$, 
we can see how the use of half, of entire frequency band, causes the decrease in the values of the curves, 
but give us considerably good values in the maximum excursion of the curve across the time. By other side,
in the case of ink drying process, the use of complete frequency band ($STD(t)$ index), 
it returns low values of maximum excursion in the curves across the time. 
The importance of excursion, in this test,
 is due to the need of significant differences between the values of two states,
during the
%when the sample start or end the ink 
drying process.

@@

Thus, at this point,
an question is evident: 
What is the best frequency band? According with the test of corn seed, 
we see that for all frequency bands, 
the best range, 
is the one with the components with lowest possible frequencies; 
but without forget that given a $STD(t)$ analysis, 
this index extract information of inner parts of material \cite{Nothdurft:05}, 
and this information decrease jointly with the decrease of frequency band,
as can be seen when compared the result in the excursion of $STD(t)$, 
with frequency components in low frequencies,
and the excursion of $\{$ $STDF(t)$ and $AVD(t)$ $\}$, 
with frequency components in high frequencies;
so that we need to choose a compromise between the desired quantity of inner information in the sample, 
the perceived illumination level and the sampling rate.

@@

In this work were presented comparisons of three dynamic laser speckle indexes,
subject to different values of sampling rate.
thus we conclude that it is important to choose an appropriate sampling rate, 
being recommendable to use the minimal sampling frequency possible to get an acceptable maximum excursion, 
in index as the $AVD$ and $STDF$,
and an illumination level in the images with good signal-noise relation,
so that the phenomenon under study can be collected in the chosen analysis frequency band.
We showed that the digitization  of speckle signal imply a restriction of frequency 
band of signal and consequently this affect the result of an speckle analysis.
And the user of a digital camera must be aware that the increase of the frame rate (fps) 
force the commercial cameras to change the perceived illumination level in the camera sensor.

>>>>

\journal{Optics and Lasers in Engineering}

@@

\title{Sampling Rate in the Dynamic Speckle Analysis}
%\tnotetext[mytitlenote]{Fully documented templates are available in the 
%elsarticle package on \href{http://www.ctan.org/tex-archive/macros/latex/contrib/elsarticle}{CTAN}.}

% Group authors per affiliation:
\author{Pujaico~Rivera, F.}
\author{Gonzalez-Pe\~na, R. J.}
\author{Braga, R. A.}

@@

\begin{abstract}
In this article, we show as the variation of sampling rate, 
in a dynamic speckle analysis, affects the value of some dynamic speckle indexes, 
to the cases of the absolute value of the differences index, 
the temporal speckle standard deviation index and the temporal speckle mean index.
We show that  the dynamic speckle index value changes its maximum excursion with 
the variation of sampling rate, affected directly by the time integration 
(exposition time) of camera.
We highlight the importance of knowing  the frequency band of analyzed phenomenon, 
in order to choose the appropriate sampling rate, 
being recommendable to use the minimal sampling rate possible
to get an acceptable maximum excursion, 
and an illumination level with good signal-noise ratio.

@@

\begin{keyword}
Sampling rate \sep
Dynamic speckle index \sep 
Dynamic speckle index \sep 
Dynamic speckle analysis
\end{keyword}

@@

%3) Resgate a problematica( Importancia do problema de pesquisa - extenda primer passo)
Thus, 
it is necessary analyze the effect of technical parameters that affect the perceived illumination level; 
in these sense,
we analyze the effect of sampling rate, 
and consequently the time exposure, in a dynamic laser speckle analysis
that use: the absolute value of the differences index, 
the temporal speckle standard deviation index and the temporal speckle mean index \cite{Nothdurft:05}.

%4) Relevancia do artigo(importancia para outros del artigo publicado)
Knowing the effect of sampling rate over an index value,
a researcher will be able to have a criteria to choose the appropriate sampling rate
for a certain monitored phenomenon. 
% Thus,
% optimizing resources when choosing the hardware specification in a system setup; 
% being in this case, the limitations relatives to illumination level and signal-noise relation in the study sample.

%5) Anuncie a hipotesis
For this purpose, we show that given a dynamic speckle test, exists an appropriate frequency band
to the sampling rate. High values of sampling rate may cause unintended consequences on the index value, 
such as the decrease of the excursion between two activity levels, given a determinate index value. 
In turn, decreasing the sampling rate promoted by the increasing of the exposure time,
will cause a reduction of the temporal speckle contrast,
 and consequently limit the possibility  to get information from the sample.

@@

\subsection{Time exposure of the camera}
\label{subsec:expositiontime}
The sampling rate ($F_s$) or acquisition time in frames per second ($fps$), 
in the camera Marlin F-033 is obtained using the 
 Table \ref{table:1}, 
\begin{table}[h!]
\centering
\begin{tabular}{||c c c c c||} 
 \hline
 $Shutter$ &  $Base$ [$\mu s$] & $Offset$ [$\mu s$] & $E$ [$ms$] & $F_s$ [$fps$]\\ [0.5ex] 
 \hline\hline
 3332  & 20  & 12  & 66.652  & 15.003  \\ 
 1665  & 20  & 12  & 33.312  & 30.019  \\ 
 1110  & 20  & 12  & 22.212  & 45.021  \\ 
 832   & 20  & 12  & 16.652  & 60.053  \\ [1ex] 
 \hline
\end{tabular}
\caption{Exposition time and sampling rate}
\label{table:1}
\end{table}
where we can see the 4 sampling frequencies that will be used in the tests;
these values were obtained using  
the shutter register value ($Shutter$), 
the time base register value ($Base$),
the exposure time offset ($Offset$) and
the effective exposure time ($E$);
 so that the exposure time ($Exposure$),
\begin{equation}
Exposure= Shutter \times Base,
\end{equation}
\begin{equation}
\frac{1}{F_s}=E= Exposure + Offset.
\end{equation}
Where,  $F_s$ is calculated in relation to $E$; being that,
the $Exposure$ represent the photography integration time and $E$ the effective time
between photographs; 
the difference between these two exposures arise from $Offset$ time, 
that is the time between end and start of a photography.
In all cases the exposure time is much bigger than $Offset$; so, we can approximate
that $F_s\approx 1/Exposure$.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Figure \ref{fig:STDtest1} presents the $STD(t)$ index in the test showed in the 
Section \ref{subsec:test1}.
\begin{figure}[ht!]
    \centering
    \begin{subfigure}{0.48\textwidth}
        \caption{$STD$ index value.}
        \includegraphics[width=\textwidth]{FPS_f11_rawSTD.eps}
        \label{fig:stdraw}
    \end{subfigure}
    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
      %(or a blank line to force the subfigure onto a new line)
    \begin{subfigure}{0.48\textwidth}
        \caption{Normalized $STD$ index value.}
        \includegraphics[width=\textwidth]{FPS_f11_norm1STD.eps}
        \label{fig:stdnorm}
    \end{subfigure}
    \caption{$STD$ index anaysis.}\label{fig:STDtest1}
\end{figure}
The Figure \ref{fig:stdraw} shows the  behavior of $STD(t)$ index, in each time $t$, 
to 4 different sampling rates. Remembering that this index uses information in the entire frequency
band ($0$ until $F_s/2$ Hz), as seen in Section \ref{sec:std}.
This index shows a different behavior in time to each sampling rate,
so that, the value of the index in each time  decreases in proportion with 
the grow of sampling rate. By other side,
Figure \ref{fig:stdnorm} shows a normalized version of $STD(t)$ index;
being the unit, the maximum value of curves; thus,
it can be seen that exists a small difference between the maximum excursion 
of the curves with different sampling rates; even so, it is possible to observe
a slight decrease of the maximum excursion in the curve with the grow of the sampling rate, 
unlike the $AVD(t)$ index.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Figure \ref{fig:STDFtest1}, presents the $STDF(t)$ index, in the test showed in the 
Section \ref{subsec:test1}.
\begin{figure}[ht!]
    \centering
    \begin{subfigure}{0.48\textwidth}
        \caption{$STDF$ index value.}
        \includegraphics[width=\textwidth]{FPS_f11_rawSTDF.eps}
        \label{fig:stdfraw}
    \end{subfigure}
    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
      %(or a blank line to force the subfigure onto a new line)
    \begin{subfigure}{0.48\textwidth}
        \caption{Normalized $STDF$ index value.}
        \includegraphics[width=\textwidth]{FPS_f11_norm1STDF.eps}
        \label{fig:stdfnorm}
    \end{subfigure}
    \caption{$STDF$ index anaysis.}\label{fig:STDFtest1}
\end{figure}
Figure \ref{fig:stdfraw} shows the behavior $STDF(t)$ index, in each time $t$, 
to 4 different sampling rates. Remembering that this index uses filtered 
information of datapack, so that the frequency
band is between $F_s/4$ and $F_s/2$ Hz. 
% of similar way of $AVD(t)$ index but with different order filter, as seen in Section \ref{sec:stdf}.
This index shows monotone decreasing behavior in time, where we observe 
a different behavior in time to each different sampling rate;
so that, the value of the index in each time decreases in proportion with 
the grow of sampling rate. By other side,
Figure \ref{fig:stdfnorm} shows a normalized version of $STDF(t)$ index;
being the unit, the maximum value of curves; thus,
it can be seen that exists a considerable difference between the maximum excursion 
of the curves with the use of sampling rate; so, it is possible to observe a 
grow of the maximum excursion when the sampling rate decrease, like the $AVD(t)$ index.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Figure \ref{fig:MEANtest2} shows the $MEAN(t)$ index,
decreasing its value
%in the test described in the Section \ref{subsec:test2};
\begin{figure}[ht!]
    \centering
    \includegraphics[width=0.5\textwidth]{FPS_Semilla_3_3diasALLMEAN.eps}
    \caption{$MEAN$ index value in the germinated corn seed.}\label{fig:MEANtest2}
\end{figure}
%We observe as the index decrease your value, 
with the increment of sampling rate, %in the datapack,
where from %so that between 
$15$ Hz to $60$ Hz, the index value reached the $20.137\%$ of its value.

@@

The matrices $STDB$ are represented using a color palette, 
that goes from dark blue (low values) to dark red color (high values), 
%representing of ascendant way 
linked to the values of activity,
%in each pixel in all matrices, as It is shown in the top of table. 
it is evident how the index values decreases with
the increment of sampling rate $F_s$.
%in each one of 8 frequency bands, 
The index values also decrease with the increment of the position of frequency band,
being  a frequency band between $0$ Hz and $3.75$ Hz with a sampling rate of $15$ hz,
the better analysis's case; in the sense of better differentiating places of lower and higher index value.

@@

%In the results seen in Section \ref{sec:numericalresults}, we can observe in 
In the Figure \ref{fig:MEANtest1} and \ref{fig:MEANtest2}, 
%that 
the indexes show a relation between the profile of mean index curve and the sampling rate of datapack. 
%How is known \cite{Nothdurft:05}, 
The temporal speckle mean index (Fig. \ref{fig:MEANtest1}) is related to 
the observed illumination level in the surface of the material \cite{Nothdurft:05} and  
correspond to the analysis of zero frequency components of signal.
%correspond to the offset in the frequency domain or frequency zero.
%zero frequency of the signal (datapack);
Thus, we can conclude that the level of illumination, perceived by the camera, 
decrease with the increment of sampling rate. 
This is because that the exposition time is modified with the alteration of sampling frequency to commercial cameras, 
%see Section \ref{subsec:expositiontime}, 
so that less lighting is used to take the picture and consequently the 
temporal speckle mean index decrease in  its value.
In this sense, it is important to be aware to choose a sampling rate
that gives us an index value superior to the noise level of test or to the quantization level of the camera.

The modification of exposition time also affects  and limits other indexes,
remember that we have a quantization level between $0$ and $255$ in the camera. 
We can see this interference in the Figures \ref{fig:AVDtest1}, \ref{fig:STDtest1}, \ref{fig:STDFtest1} and \ref{fig:INDEXtest2}, 
where the $AVD(t)$, $STD(t)$ and $STDF(t)$ indexes decrease their values in concordance with the decrease of exposition time.
Other way in that  the sampling rate affects the values of indexes,
can be seen in the limitation of
%It is that, it limits 
the frequency band of an analyzed signal; for example,
a sampling rate $F_s$, by the Nyquist theorem \cite{Nyquist,Shannon}, 
causes  the limitation of  frequency band %of analyzed signal (datapack)  will be 
between $0 Hz$ and $F_s/2~Hz$.
Thus, in this context we have an index as $STD(t)$ that uses information between $\langle \left. 0, F_s/2 \right ] Hz$, 
while other  indexes as the $AVD(t)$ and the $STDF(t)$ index, use information of half frequency band, 
between $\left [ F_s/4, F_s/2 \right ] Hz$.
In the comparison between $STD(t)$ vs  $\{$ $STDF(t)$ and $AVD(t)$ $\}$, 
we can see how the use of half, of entire frequency band, causes the decrease in the values of the curves, 
but give us considerably good values in the maximum excursion of the curve across the time. By other side,
in the case of ink drying process, the use of complete frequency band ($STD(t)$ index), 
it returns low values of maximum excursion in the curves across the time. 
The importance of excursion, in this test,
 is due to the need of significant differences between the values of two states,
during the
%when the sample start or end the ink 
drying process.

@@

Thus, at this point,
a question is evident: 
What is the best frequency band? According with the test of corn seed, 
we see that for all frequency bands, 
the best range is the one with the components with lowest frequencies; 
but without forget that given a $STD(t)$ analysis, 
this index extract information of inner parts of material \cite{Nothdurft:05}, 
and this information decreases jointly with the decrease of frequency band,
as can be seen when compared the result in the excursion of $STD(t)$, 
with components in low frequencies,
and the excursion of \{$STDF(t)$ and $AVD(t)$\}, 
with components in high frequencies;
so that we need to choose a compromise between the desired quantity of inner information in the sample, 
the perceived illumination level and the sampling rate.

@@

In this work were presented comparisons of three dynamic laser speckle indexes,
subject to different values of sampling rate.
thus we conclude that it is important to choose an appropriate sampling rate, 
being recommendable to use the minimal sampling rate possible to get an acceptable maximum excursion, 
in index as the $AVD$ and $STDF$,
and an illumination level in the images with good signal-noise relation,
so that the phenomenon under study can be collected in the chosen analysis frequency band.
We showed that the digitization  of speckle signal imply a restriction of frequency 
band of signal and consequently this affect the result of an speckle analysis.
And the user of a digital camera must be aware that the increase of the frame rate (fps) 
force the commercial cameras to change the perceived illumination level in the camera sensor.
